### 2025-01-14 NLP/exercises.tex
Small exercise updates.

\begin{exercise}{Teacher/Student}
  Explain the teacher/student signals approach in educational NLP and why it is better than pure audio content.

  \begin{solution}
    \begin{itemize}
        \item \textbf{Teacher signals}: Provide detailed instructions and explanations.
        \item \textbf{Student feedback}: Allows iterative learning and personalization.
        \item \textbf{Better than audio}: Interaction and adaptivity enhance understanding and retention compared to static audio content.
    \end{itemize}
  \end{solution}
\end{exercise}

@@

\begin{exercise}{Edit distance}\label{ex:edit-distance}
  \begin{enumerate}
    \item Define the Minimum Edit Distance.
    \item Calculate the Minimum Edit Distance for "TAC" vs. "CAT".
    \item What are the possible word outcomes?
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
        \item The Minimum Edit Distance is the minimum number of operations (insertion, deletion, substitution) required to transform one string into another.
        \item \[\begin{array}{c|c|c|c|c}
            &  & C & A & T \\
            \hline
            & 0 & 1 & 2 & 3 \\
            T & 1 & 1 & 2 & 2 \\
            A & 2 & 2 & 1 & 2 \\
            C & 3 & 2 & 2 & 2 \\
        \end{array}\]
        \item CAT, TAT, TAC, CAC
    \end{enumerate}
  \end{solution}
\end{exercise}

>>>>

@@

\begin{exercise}{Edit distance}\label{ex:edit-distance}
  \begin{enumerate}
    \item Define the Minimum Edit Distance.
    \item Calculate the Minimum Edit Distance for "TAC" vs. "CAT".
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
        \item The Minimum Edit Distance is the minimum number of operations (insertion, deletion, substitution) required to transform one string into another.
        \item The Minimum Edit Distance for "TAC" vs. "CAT" is 2.
    \end{enumerate}
  \end{solution}
\end{exercise}
